### 2016-11-08 thesis/intro/intro.tex
tmp commit

When a satiety-controlling hormone, such as leptin, reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.

Firstly, when an orexogenic \gls{npy}/\gls{agrp} neurons are stimulated,

>>>>

When a satiety-controlling hormone, such as leptin, reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both orexogenic and anorexogenic neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.

Firstly, when an orexogenic \gls{npy}/\gls{agrp} neurons are stimulated, both \gls{npy} and \gls{agrp} are produced in the cell.
Both \gls{npy} and \gls{agrp} are neuropeptides that sends a signal to increase food intake and decrease energy expenditure.
\gls{npy} was first discovered by \citet{Tatemoto1982}, and later associated with altered eating behaviour by \citet{Clark1984}.
Agouti protein is a protein normally expressed in the skin where it affects the pigmentation, and was first observed over 100 years ago by \citet{Castle1910} in mice that had yellow, or agouti-coloured coat.

It was later found the ubiquitous expression of the protein was caused obesity (citation)

The \gls{npy} and \gls{agrp} neuropeptides are recognised by the downstream neurons via the \gls{nyr} and \gls{mcr}.
